---
title: "Who is Smarter Preliminary Analysis"
author: "Peter Williams"
date: "4/21/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### The Data
The survey data used in this report was gathered from students during the Spring semester of 2019 at Utah Valley University. 

#### Cleaning the Data
Exporting data from qualtrics results in a lot of useless information (such as geographical location) that needs to be removed. Also, because the survey questions are not "forced response", a lot of elements are missing from the data set. The unneccessary variables were removed as well as the NAs with the following scripts:  

* "survey_tidying_script.R"  

* "removing_missing_values_SP2019.R"

#### Analyzing the data
Because we don't have data about the GPA yet, I ran a chi-squared (two-variable), to determine if their was a relationship between gender and perceived intelligence (measured with a factored question "who is smarter, you or your group member?". The results of the chi-squared are as follows:
```{r chi-squared, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(gmodels)
df = read.csv("../tidy_data/SP2019_survey_no.NAs.csv")
df = df %>%
  mutate(Who_is_smarter. = factor(Who_is_smarter.))

CrossTable(df$gender2, df$Who_is_smarter., 
           fisher = TRUE, 
           chisq = TRUE, 
           expected = TRUE, 
           sresid = TRUE,
           format = "SPSS",
           prop.c = TRUE,
           prop.t = FALSE,
           prop.chisq = FALSE)
```


