---
title: "Prevalence_Concept_Threshold_Variables"
author: "pwilliams"
date: "3/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(modelr)
```
# Variables

## These are some variables for determining diameter of stimuli circle  

+ **Convert angle of diameter(3.7ยบ) to centimeters:**  

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
x = 184*tan(1.35*(pi/180))
paste(x,"cm")
```

+ **There is an imaginary inner circle upon which individual stimuli are evenly placed. Convert angle of diameter (12.6) for the inner circle to centimeters:**

```{r}
x1 = 92*tan(12.6*(pi/180))
paste(x1,"cm")
```

+ **There are 6 circles surrounding the center circle, which means each stimulus circle has its own respective coordinate on the imaginary circle.:**

```{r echo=FALSE, message=FALSE, warning=FALSE}
angbtwn = 2*pi/6 # in radians
xcoords = c()
ycoords = c()
for(i in 0:5) {
  xcoords[i+1] = x1*cos(i*angbtwn)
  ycoords[i+1] = x1*sin(i*angbtwn)
}
coords = cbind(xcoords, ycoords)
coords
```

### Determining variablility of our stimuli color:  

* 60.8%- 99.6% Blue   
  + Middle = 50-0-205, 80.3%   
  + +/- 19.3%    
* **Low** = -5, -5, -2, 2, 5, 5  
  + *Mid Shift* = -14.3% -14.3%
* **Mid** = -10, -8, -4, 4, 8, 10  
  + *Mid Shift* = -9.3% - 9.3% 
* **High** = -15, -13, -10, 10, 13, 15  
  + *Mid Shift* = -4.3% - 4.3 %  
  
**Trials**
900 trials, 18 blocks of 50:  
 + 300 low  
 + 300 mid  
 + 300 high
 
 
### Target Stimuli

Purple|Blue
------|-----
100-0-155 (60.8% Blue)| 50-0-205 (80.3% Blue)
51-0-204 (80% Blue) | 1-0-254 (99.6% Blue)


### RGB values for our target stimuli:

```{r echo=FALSE, warning=FALSE, message=FALSE}
my_colors = read.csv("./Practice_R/mycolors.csv")
head(my_colors)
tail(my_colors)
```

Set the low variability blue values
```{r echo=FALSE, warning=FALSE, message=FALSE}
# determine coordinates to set ranges for low variability ####
k = c()
for(i in 0:7) {
  k = c(k,i*(99/7) + 155)
}
k = round(k, 0)
# determine the ranges of blue values for the low variability 
low.v.blue.val = data.frame(Min = k[1:7], Max = k[2:8])
low.v.blue.val = mutate(low.v.blue.val, int.range = (Max - Min)/6)
# make min and max columns one and two
colnames(low.v.blue.val)[1] = "B1"
colnames(low.v.blue.val)[2] = "B6"
# add in outer stimuli columns 
low.v.blue.val$B2 = low.v.blue.val$B1 + low.v.blue.val$int.range
low.v.blue.val$B3 = low.v.blue.val$B2 + low.v.blue.val$int.range
low.v.blue.val$B4 = low.v.blue.val$B3 + low.v.blue.val$int.range  
low.v.blue.val$B5 = low.v.blue.val$B4 + low.v.blue.val$int.range
# re-order the data set
low.v.blue.val = low.v.blue.val[,-3]
low.v.blue.val = low.v.blue.val[c(1,3:6,2)]
# round the values
low.v.blue.val = round(low.v.blue.val, 0)

low.v.blue.val
```
Set the mid variability blue values
```{r echo=FALSE, warning=FALSE, message=FALSE}
m = c()
for(i in 0:5) {
  m = c(m,i*(99/5) + 155)
}
m = round(m, 0)
# determine the ranges of blue values for the low variability 
mid.v.blue.val = data.frame(Min = m[1:5], Max = m[2:6])
mid.v.blue.val = mutate(mid.v.blue.val, int.range = (Max - Min)/6)
# make Min -> B1
colnames(mid.v.blue.val)[1] = "B1"
# add in outer stimuli columns 
mid.v.blue.val$B2 = mid.v.blue.val$B1 + mid.v.blue.val$int.range
mid.v.blue.val$B3 = mid.v.blue.val$B2 + mid.v.blue.val$int.range
mid.v.blue.val$B4 = mid.v.blue.val$B3 + mid.v.blue.val$int.range  
mid.v.blue.val$B5 = mid.v.blue.val$B4 + mid.v.blue.val$int.range
# make min and max columns one and two
colnames(mid.v.blue.val)[2] = "B6"
# re-order the data set
mid.v.blue.val = mid.v.blue.val[,-3]
mid.v.blue.val = mid.v.blue.val[c(1,3:5,2)]
mid.v.blue.val = round(mid.v.blue.val, 0)
mid.v.blue.val
```
Set the high variability blue values
```{r echo=FALSE, message=FALSE, warning=FALSE}
# set high variability blue values ####
B1min = 155
B1max = 155 + .5*99
B2min = 155 + .25*99
B2max = 155 + .75*99
B3min = 155 + .5*99
B3max = 254

high.v.blue.val = data.frame(B1 = c(B1min, B2min, B3min), B6 = c(B1max, B2max, B3max))
high.v.blue.val = mutate(high.v.blue.val, int.range = (B6 - B1)/6)
# add in outer stimuli columns 
high.v.blue.val$B2 = high.v.blue.val$B1 + high.v.blue.val$int.range
high.v.blue.val$B3 = high.v.blue.val$B2 + high.v.blue.val$int.range
high.v.blue.val$B4 = high.v.blue.val$B3 + high.v.blue.val$int.range  
high.v.blue.val$B5 = high.v.blue.val$B4 + high.v.blue.val$int.range

# re-order the data set
high.v.blue.val = high.v.blue.val[,-3]
high.v.blue.val = high.v.blue.val[c(1,3:5,2)]
high.v.blue.val = round(high.v.blue.val, 0)
high.v.blue.val
```